---
title: "Package Far"
author: "Takashi Sendor"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a very simple package to explore 2013-2015 data from the National Highway Traffic Safety Administration (NHTSA) Fatality Analysis Reporting System (FARS). This package was written for the Week 4 final assignment for the "Building R Packages" course on Coursera, as part of the Johns Hopkins University "Mastering Software Development in R" specialization.

## The Data

The data in this package come from the National Highway Traffic Safety Administration (NHTSA) Fatality Analysis Reporting System (FARS) data. It lists the fatal vehicle crashes in the United States for each year; each crash observation can has as many as 50 features.

With this package, the available years of data are: 2013-2015.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Summarizing FARS Data

The fars_summarize_years() function take the same argument as the fars_read_years(), and produces a summary of the simple counts of fatalities by month and year:

```{r, echo=FALSE}
fars_summary <- fars_summarize_years(2013:2015)
fars_summary
```

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
